
\section{Description of the work}
\subsection{Aims and Objectives}
The aim of this project was to design, build and analyse a system for refining a mesh by combining a method derived from the fields of AI or machine learning with a method relying purely on information already present in the model. The desirable end result will be a hybrid method of meshing which effectively prioritises those areas of importance whilst incurring a reduced computational cost.\\

\noindent
The project can be broken down into thee main areas of research and implementation which have the following high level objectives:\\ 

\begin{enumerate}[label=\Alph*]

\item Research and implement both a traditional refinement procedure using data present within the model and an approach using techniques from AI developed and used by either industry or academia. These algorithms should be able to run independently on a set of example models.

\item Secondly a process needs to be devised to combine the two re meshing methods to varying degrees. This will make it possible to evaluate and compare the effects of a hybrid meshing against each of the individual methods for a range of models. Through this it should be possible to establish whether or not there is potential benefit to using a hybrid approach and if so to what extent.

\item The third objective will be to research and implement justifiable metrics for assessing the quality of a given mesh, this will allow objective comparisons to be made for the resulting meshes.


% This will allow for a much greater range of hybrid variations to be tried without requiring inspection from an expert. 
\end{enumerate}

\subsection{System specification}
To demonstrate success in achieving the objectives of the project it is important to have traceability from the requirements through to the solution and lastly verification and validation. This section describes the systems initial \textit{functional requirements} (what the system will do) and \textit{non-functional} requirements (its constraints) based upon evaluation of the research conducted in conjunction with discussions with the project supervisor: Dr Jason Atkin. Functional requirements have primarily been listed under their respective high level subsystems that are responsible for encapsulating their functionality. \\ 

\noindent
Although it has not been developed as part of the project the application responsible for solving the finite element models has been included as part of the systems requirements since it highly influences the overall scope of the project and much of the design associated with other subsystems which were developed for the project. \\ 

\subsection{Functional Requirements}

\begin{enumerate}
\item FE integration: System will be able to interface with a third party finite element application

\begin{enumerate}
\item The finite element applications solver must be able to solve a mesh based on its model configuration.
\item The finite element applications solver must be able to execute a model programmatically
\item The finite element applications solver must be able to output stress data at different points on the mesh.
\item The finite element application will provide a graphical representation of the model.
\item It will be possible to manipulate the model that the finite element application uses programmatically.
\item It should be possible to manipulate the model that the finite element application uses from within its graphical user interface.
\end{enumerate}

\item Mesh refinement: System will be able to perform different kinds of finite element mesh refinement

\begin{enumerate}
\item The system will be able to refine a finite element mesh using a stress based refinement method.

\item The system will be able to refine a finite element mesh using a non-stress based refinement method.

\item A non stress based refinement method will adapt the mesh using background information about mesh design which has been previously trained.

\item The system will be able to combine the two methods to produce a coherent mesh which the FE application is able to successfully solve in order to obtain results for stress and displacement.

\item The system will be able to combine both methods to varying degrees that will be performed automatically by the system without direct user intervention.
\item The system will re mesh using both stress and non-stress based refinement using quadrilateral elements.

\item System will adapt weighting associated with each method based upon the metrics computed for the mesh in the systems previous iteration.
\end{enumerate}

\item Quality assessment: System will provide the operator with results about the quality of meshes based on metrics obtained from research.

\begin{enumerate}
\item An assessment will be conducted automatically for every mesh iteration that occurs.

\item System will assess quality based on a variety of metrics to ensure overall robustness of measurement. 

\item The metrics will be computed for both individual element within the model and for the entire mesh.
\end{enumerate}
\end{enumerate}

\subsection{Non-Functional Requirements}


\textbf{Design:} The system architecture will be developed using the object oriented design principals of SOLID to allow for clear interfaces between the different functional components. Functional programming practices will be adopted through use of the .NET Language Integrated Query or LINQ framework. This will help to simplify the code and improve reliability by removing unnecessary state from the program. Where functions and classes are written their length will be kept to a minimum to reduce complexity and allow for reuse wherever possible. \\ 

\noindent
\textbf{Documentation:} The system will be comprehensively documented at both a code level and at an architecture level. At a code level C\# doc comments will be written to provide a comprehensive summary of each function. This will allow the tool Doxygen \cite{Doxygen} to generate a full set of developer documentation upon completion of the software implementation which will be included as an appendix. Ensuring that the majority of information is present within doc comments will also help to promote a reduction of loose comments within the code and hence function size. \\

\noindent
\textbf{General applicability:} In order to demonstrate that hybrid methods are a feasible means of approaching meshing problems the resulting software should be able to successfully execute on a range of models with varying geometry. The range of geometries should be representative of typical structural variation encountered by engineers.